Using Monte Carlo Algorithms to Achieve Resiliency \& Performance at Scale for Linear and Nonlinear Solver Applications

### 2016-01-26 doc/ecp/pres.tex
Finished all but timeline.

\begin{frame}{Building on ASCR Funding}

  \underline{\bf Trilinos}
  \begin{itemize}
  \item Provides abstract solver interface for MCLS
  \item Provides build system for Alea and MCLS
  \item Provides data structures and utilities for Alea and MCLS
  \item Provides testing harness for MCLS
  \end{itemize}

  \underline{\bf xSIM}
  \begin{itemize}
  \item Simulator to test for hard error detection and remediation
  \end{itemize}

@@

\begin{frame}{Building on ASCR Funding}

>>>>

\begin{frame}{Trilinos Enables Inter-Operability}

  \begin{itemize}
  \item Provides abstract numerical algorithms
    \begin{itemize}
    \item solver interfaces
    \item operator/vector interfaces
    \item preconditioner interfaces
    \end{itemize}
    \vfill
  \item Provides build system (TriBITS) for Alea and MCLS
    \vfill
  \item Provides data structures and utilities for Alea and MCLS
    \vfill
  \item Provides testing harness for MCLS
  \end{itemize}

@@

\begin{frame}{xSIM Development and Fault Analysis Supported by MCREX}

  \begin{itemize}
  \item Use xSIM to model communication performance of MPI messaging
    \begin{itemize}
    \item Latency, bandwidth, contention, routing, and rendevous protocol
    \item Star, ring, mesh, torus, twisted torus, and tree topologies
    \item Hierarchical combinations of topologies, e.g. on-chip, on-node,
      off-node
    \end{itemize}
  \item Also used to simulate hard errors to test for detection and recovery
  \end{itemize}
  \vfill
  \begin{figure}
    \centering
    \includegraphics[height=.4\textwidth]{xsim}
  \end{figure}

\begin{frame}{Using XSTACK Technologies Developed by XPRESS}
